Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1214

%%%----Versions-----------------------------
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{amsthm}
\usepackage{stackrel}
\usepackage[backref=section]{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

@@

%term of the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 

@@

%\subsection{Model}

@@

\subsection{OU Semigroup}
    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
    It is known that $(T_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
    discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $A_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    Thus, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
    the order of the function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
$
	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|
$
$
	Q f:= Q_{\kappa_f}f.
$
    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
    Let $X$ be the super OU-process discussed in Subsection \ref{ss:1.1}.
    Its branching mechanism $\psi$ can be extended to $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$:
 $$\psi(z) := -\alpha z + z^{1+\beta}, \quad z\in \mathbb C_+.$$ 
    According to the analysis in Subsection A.1, 
    $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
    Write $\psi_0(z) := \psi(z) + \alpha z$. Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
    For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.

\subsection{Main Result}
We will use $\mathcal M_c(\mathbb R_d)$ to denote the space of all
finite Borel measures of compact support on $\mathbb R^d$.
In this subsection, we will give the main results of this paper. 
%Suppose $\mu\in \mathcal M_c(\mathbb R_d)$ has compact support.
\subsubsection{Large branching rate}

For each $p\in \mathbb{N}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in 
%  $L^{1+\gamma}(\mathbb{P}_{\mu})$, 
$L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\mu\in \mathcal M_c(\mathbb R_d)$,
  thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for 
%     any $\gamma\in (0, \beta)$,
any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
     as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$

     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. 
 \end{thm}
For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$.
 \begin{rem}
%    If $\kappa_f=0$, 
Let $f \in \mathcal{P}$.  If $\kappa_f=0$, 
    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},  
%    for any $\gamma\in (0, \beta)$, as $t\rightarrow \infty$
for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$, as $t\rightarrow \infty$,
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{rem}

\subsubsection{Critical branching rate}
    For $f\in \mathcal{P}$, define
\[
    \tilde{m}[f]
    := \langle(-i\phi)^{1+\beta},\varphi\rangle
\]
    where
\[
    \phi(x)
    =\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).
\]
    Denote by $D$ the extinction event of the super OU-process.
\begin{thm}
\label{Theorem12}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, 
%    then, under 
   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under 
    $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
    \xrightarrow{d} \eta_1, 
    \quad t\rightarrow \infty,
\]
    where $\eta_1$ is a $(1+\beta)$-stable random variable with
\[
    \mathbb{E} [e^{i\theta \eta_1}]
    =\exp(\tilde{m}[\theta f]), 
    \quad \theta\in \mathbb R.
\]
\end{thm}

@@

For $f\in \mathcal{P}$, define
\[
    m[f]
    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx
\]
\begin{thm}
\label{Theorem13}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, 
%    then, under 
   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under 
    $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
    where $\eta_2$ is a $(1+\beta)$-stable random variable with 
    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
\end{thm}

@@

 In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$. 
 %Denote by $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite Borel measures on $\mathbb{R}^d$ with compact support.
	For all $0 \leq a_1 \leq a_2 <\infty$ and  random variable $Y$ with finite mean, define
$
   	\mathcal I_{a_1}^{a_2} Y
    := \mathbb P[Y|\mathscr F_{a_2}] - \mathbb P[Y|\mathscr F_{a_1}].
$
\begin{lem}
\label{lem: control pair for P(M>lambda)}
    There is a $(1+\beta)$-control-pair $(R,S)$ such that for all $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we have
\[
    \mathbb P_\mu ( |\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
\]
\end{lem}

@@

\begin{lem}\label{lemma26}
%    $(H^p_t)_{t\geq 0}$ is a martingale with respect to $(\mathscr F_t)$.
    For any $\mu\in \mathcal M_c(\mathbb{R}^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
    Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $\gamma\in (0, \beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
\[
    H_{\infty}^p
    :=\lim_{t\rightarrow \infty}H_t^p
\]
exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
\end{lem}
\begin{proof}
%   It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a martingale.
  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb{R}^d)$.

>>>>

%%%----Versions-----------------------------
% supclt1213.tex 2018/12/13 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{amsthm}
\usepackage{stackrel}
\usepackage[backref=section]{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

@@

@@

@@

\subsection{OU Semigroup}
    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
 %   For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$,
  For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
    let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    %p \in \mathbb{N}_0^{d}.
    p \in \mathbb{Z}_+^{d}.
\end{equation}
    It is known that $(T_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
    discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $A_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb Z_+^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    Thus, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of the function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
%$
%	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|
%$
\begin{equation}\label{Q_k}
Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
\end{equation}
and
%$
%	Q f:= Q_{\kappa_f}f.
%$
\begin{equation}\label{Q}
Q f:= Q_{\kappa_f}f.
\end{equation}

    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
\subsection{}
    Let $X$ be the super OU-process discussed in Subsection \ref{ss:1.1}.
    Its branching mechanism $\psi$ can be extended to $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$:
 $$\psi(z) := -\alpha z + z^{1+\beta}, \quad z\in \mathbb C_+.$$
    According to the analysis in Subsection A.1,
    $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
   % Write $\psi_0(z) := \psi(z) + \alpha z$.
   Write $\psi_0(z) := \psi(z) + \alpha z=z^{1+\beta}$.
  %  Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.
   Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}=(1+\beta)z^\beta$.
    For all $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$, the value of the L\'evy exponent of the infinite divisible random variable $\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

\subsection{Main Result}
We will use $\mathcal M_c(\mathbb R_d)$ to denote the space of all
finite Borel measures of compact support on $\mathbb R^d$.
In this subsection, we will give the main results of this paper.
\subsubsection{Large branching rate}

%For each $p\in \mathbb{N}_+^d$, we define
For each $p\in \mathbb{Z}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
   $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\mu\in \mathcal M_c(\mathbb R_d)$,
  thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for
any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
     as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$

     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{thm}
For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$.
 \begin{rem}
Let $f \in \mathcal{P}$.  If $\kappa_f=0$,
    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$, as $t\rightarrow \infty$,
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{rem}

\subsubsection{Critical branching rate}
    For $f\in \mathcal{P}$, define
\[
    \tilde{m}[f]
    := \langle(-i\phi)^{1+\beta},\varphi\rangle
\]
    where
\[
    \phi(x)
    =\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).
\]
    Denote by $D$ the extinction event of the super OU-process.
\begin{thm}
\label{Theorem12}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$,
   then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under
    $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
    \xrightarrow{d} \eta_1,
    \quad t\rightarrow \infty,
\]
    where $\eta_1$ is a $(1+\beta)$-stable random variable with
\[
    \mathbb{E} [e^{i\theta \eta_1}]
    =\exp(\tilde{m}[\theta f]),
    \quad \theta\in \mathbb R.
\]
\end{thm}

@@

For $f\in \mathcal{P}$, define
\[
    m[f]
    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx.
\]
\begin{thm}
\label{Theorem13}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$,
   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under
    $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
    where $\eta_2$ is a $(1+\beta)$-stable random variable with
    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
\end{thm}

@@

 In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
	For all $0 \leq a_1 \leq a_2 <\infty$ and  random variable $Y$ with finite mean, define
%$
%  	\mathcal I_{a_1}^{a_2} Y
%   := \mathbb P[Y|\mathscr F_{a_2}] - \mathbb P[Y|\mathscr F_{a_1}].
%$
$$
	\mathcal I_{a_1}^{a_2} Y
  := \mathbb P_\mu[Y|\mathscr F_{a_2}] - \mathbb P_\mu[Y|\mathscr F_{a_1}].
$$

\begin{lem}
\label{lem: control pair for P(M>lambda)}
    There is a $(1+\beta)$-control-pair $(R,S)$ such that for all $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we have
\[
    \mathbb P_\mu ( |\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
\]
\end{lem}

@@

\begin{lem}\label{lemma26}
    For any $\mu\in \mathcal M_c(\mathbb{R}^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$.
    Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for any $\gamma\in (0, \beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$, we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
\[
    H_{\infty}^p
    :=\lim_{t\rightarrow \infty}H_t^p
\]
exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
\end{lem}
\begin{proof}
  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb{R}^d)$.

    There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$,
   we get, for $\gamma\in [\gamma_0, \beta)$, that there exists
    a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
\[
 	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
    \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
    =C_{\gamma, \mu, p}, \quad t\geq 0.
\]
   For any $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$, note that
\[
	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
	\leq\|H_t^p\|_{\mathbb P_\mu;1+\gamma_0}
	<C_{\gamma_0, \mu, p},
	\quad t\geq 0.
\]

   Hence, for each $\gamma \in (0,\beta)$ and any $\mu\in \mathcal M_c(\mathbb{R}^d)$,
    the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
\end{proof}
